Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-04-18 manuscript/manuscript.tex
small changes to notation

First, let us review how the KS statistic is typically computed for a sample
with no serial dependence with fitted parameters.
Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
distribution fitted onto $X_t$, and let 
$F_n$ denote the empirical distribution function based on $X_1,...,X_n$.
Let
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the
goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta)|.
\end{equation*}

@@

We note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x)),
\end{equation*}
\jy{clean up the notations. Has $F$ been defined yet? do you need cdf?}
where $F(x)$ is the true cdf (under the null $F(x) = F(x, \theta_0)$ for some
true parameter $\theta_0$).

>>>>

First, let us review how the KS statistic is typically computed for a sample
with no serial dependence with fitted parameters.
Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
distribution $F(x; \hat\theta_n)$ fitted onto $X_t$, and let 
$F_n$ denote the empirical distribution function based on $X_1,...,X_n$.
Let
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}

Then, the
goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta)|.
\end{equation*}

@@

We note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x)).
\end{equation*}
\jy{clean up the notations. Has $F$ been defined yet? do you need cdf?}
\mc{addressed}
